A lottery model of density-dependent selection

### 2017-10-25 manuscript.tex
latest

In MacArthur's view, selection at high densities is ``$K$-selection'', such that in ``crowded populations ... fitness is $K$''. MacArthur's argument is based on general equations for density-regulated population growth
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2),
\end{equation}
where, by definition, each

@@

>>>>

Given the 
For MacArthur, in ``crowded populations ... fitness is $K$'' \citep[pp. 149]{macarthur_1967}. The argument  is quite general,

 for density-regulated population growth a community with two types

MacArthur's argument is based on very general 
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2),
\end{equation}
where $n_1$ and $n_2$ are the respective densities of the two types, and the growth rates $f_1$ and $f_2$ decrease with both $n_1$ and $n_2$.

 the environmental carrying capacities for each type are defined by $f_1(K_1,0)=0$

@@

Yet the $r$/$K$ scheme is strikingly incompatible with the  model of selection
